---
title: "Tien_Levy_Replication"
output:
  pdf_document: default
  html_document: default
date: "2023-11-19"
---

Before running the codes, make sure the two files are in the working directory:
1. "GLevy_JOP_Data.csv" 
from: https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/0Y1E2B

and 

2. "conjacp.R"
from: https://github.com/flavienganter/preferences-conjoint-experiments/blob/main/Functions/conjacp.R

```{r setup, include=FALSE, warning=FALSE, messages = FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width = 100)
```

```{r}
rm(list = ls())

library(cjoint) #will also need library(cregg) but override AMCE function in cjoint so attach and detach each use of cregg
library(stats19) 
library(tidyverse)
library(Amelia)
library(plm)
library(scales)
library(foreign)
library(lmtest)
library(ggthemes)
library(pals)

#import
#https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/0Y1E2B
df <- read.csv("GLevy_JOP_Data.csv")

#establish baselines for conjoint AMCE analysis
baselines <- list()
baselines$Age <- "25"
baselines$Gender <- "Man"
baselines$"Education Level" <- "Primary School"
baselines$Recruitment <- "Ideology"
baselines$"Reputation According to the Troops" <- "Good Example"
baselines$"Military Success" <- "Won almost all battles"
baselines$Crime <- "Killing"
baselines$"Target of the Crime" <- "Enemy Informants"
baselines$"Type of Involvement in the Crime" <- "Decided to commit on his/her own"
baselines$"Attitude Toward the Crime" <- "Reluctant"

#establish factor order so conjoint levels in correct order
df$Age <- factor(df$Age, levels=c("25", "47", "68"))
df$Gender <- factor(df$Gender, levels=c("Man", "Woman"))
df$Education.Level <- factor(df$Education.Level, levels= c("Primary School", "Secondary School", "Associate Degree", "University"))
df$Recruitment <- factor(df$Recruitment, levels= c("Ideology", "A Job", "Forced Recruitment"))
df$Reputation.According.to.the.Troops <- factor(df$Reputation.According.to.the.Troops, levels= c("Good Example", "Kind", "Power-hungry", "Unjust"))
df$Military.Success <- factor(df$Military.Success, levels=c("Won almost all battles", "Won half of battles", "Won few battles"))
df$Crime <- factor(df$Crime, levels=c("Killing", "Sexual Violence"))
df$Target.of.the.Crime <- factor(df$Target.of.the.Crime, levels=c("Enemy Informants", "People living in an area that supported the enemy ", "People living in an area controlled by the enemy"))
df$Type.of.Involvement.in.the.Crime <- factor(df$Type.of.Involvement.in.the.Crime, levels=c("Decided to commit on his/her own", "Did not prevent someone else from committing", "Followed an order to commit", "Ordered someone else to commit"))
df$Attitude.Toward.the.Crime <- factor(df$Attitude.Toward.the.Crime, levels=c("Reluctant", "Enthusiastic"))

##make non-conjoint variables numeric
df$ResAge <- as.numeric(as.character(df$ResAge))
df$ResGender <- as.numeric(as.character(df$ResGender))
df$Edu <- as.numeric(as.character(df$Edu))
df$Ideology <- as.numeric(as.character(df$Ideology))
df$Income <- as.numeric(as.character(df$Income))
df$Ideology <- as.numeric(as.character(df$Ideology))
df$Urban <- as.numeric(as.character(df$Urban))
df$CivilianAttitude <- as.numeric(as.character(df$CivilianAttitude))
df$ExposureVictimizatio <- as.numeric(as.character(df$ExposureVictimizatio))
df$Duque <- ifelse(df$WhoVote2018==1, 1, 0)
df[df$Género==3] <- NA #option of prefer not to say 
#Tien: what does this line do? there is no "Genero" variable

#take out . from conjoint column names with multiple words
colnames(df)[colnames(df)=="Education.Level"] <- "Education Level"
colnames(df)[colnames(df)=="Reputation.According.to.the.Troops"] <- "Reputation According to the Troops"
colnames(df)[colnames(df)=="Military.Success"] <- "Military Success"
colnames(df)[colnames(df)=="Target.of.the.Crime"] <- "Target of the Crime"
colnames(df)[colnames(df)=="Type.of.Involvement.in.the.Crime"] <- "Type of Involvement in the Crime"
colnames(df)[colnames(df)=="Attitude.Toward.the.Crime"] <- "Attitude Toward the Crime"

#remove conjoint non-responses
FC <- df[!(is.na(df$selected_FC)),] #removes FC NA (1488 didn't answer i.e. 11.7 percent)
Rating <- df[!(is.na(df$selected_Rating)),] #removes Rating NA (832 NAs i.e. 6.5%)
```


```{r}
####Main Text Figure 2 + Appendices 1-3: Conjoint Results####

#Figure 2 (Main) + Table A.1: FC Results
FC_Main <- amce(selected_FC ~ Age + Gender + `Education Level` + Recruitment + `Reputation According to the Troops` + `Military Success` + Crime + `Target of the Crime` + `Type of Involvement in the Crime` + `Attitude Toward the Crime`, data= FC, cluster=TRUE, respondent.id="Response.ID", baselines=baselines)

fg2 <- plot(FC_Main, xlab="Change in Pr(Prefer Candidate)", xlim=c(-.2,.2), ci=.95, colors="black", group.order= c("Age", "Gender", "Education Level","Recruitment", "Reputation According to the Troops", "Military Success", "Crime", "Target of the Crime", "Type of Involvement in the Crime", "Attitude Toward the Crime"), text.size=13)

ggsave(file="fg2.eps", width=11, height=12.5, dpi=300)
```

Extension I: Bounds for Majority Preference Inference

```{r}
#How many attributes, how many profiles

attributes = c("Age", "Gender", "Education Level", "Recruitment", "Reputation According to the Troops", "Military Success", "Crime", "Target of the Crime", "Type of Involvement in the Crime", "Attitude Toward the Crime")

length_unique = function(x){
  return( length(unique(x)))
}

X <- sapply(df[attributes], length_unique)
K <- prod(X)

#bound function is modified from: https://dataverse.harvard.edu/file.xhtml?fileId=5254587&version=1.1

AMCE_bound <- function(pi, tau, se_pi = NULL) {
  
  K = K
  # compute lower and upper bound according to proposition 2
  l <- max(((pi * tau * K) + tau) / ((K * (tau - 1)) + tau), 0)
  u <- min(((pi * tau * K) + (K * (tau - 1))) / ((K * (tau - 1)) + tau), 1)
  bounds <- c(l, u)
  names(bounds) <- c("lower", "upper")
  # compute 95% confidence set for the bounds
  if (is.null(se_pi)) {
    # just return analytic bounds if no standard error is provided
    output <- bounds
  } else if (class(se_pi)=="numeric" & length(se_pi)==1) {
    # delta method-computed standard error (same for upper and lower bound)
    se <- sqrt(((tau * (K - 1)) / ((K * (tau - 1)) + tau))^2 * se_pi^2)
    # confidence interval 
    ci.lower = max(0, l + (qnorm(0.025) * se))
    ci.upper = min(1, u + (qnorm(0.975) * se))
    ci <- c(ci.lower, ci.upper)
    names(ci) <- c("lower", "upper")
    output <- list(bounds, ci)
    names(output) <- c("analytic_bounds", "ci_95")
  } else {
    # return an error if standard error is entered incorrectly
    cat("Please provide a numeric value for se_pi \n")
    stop()
  }
  return(output)
}
```

```{r}
#build two vectors with pi and corresponding tau
#then: mapply(AMCE_bound, pi_vec, tau_vec)

estlist <- function(x){
FC_Main$estimates[[x]][1,1:ncol(FC_Main$estimates[[x]])]
  }

pi_vec <- as.numeric ( unlist ( sapply(c(1:length(attributes)), estlist) ) ) 

tau_vec <- rep(0, length(attributes))

for (i in 1:length(attributes)) {
  tau_vec[i] = ncol ( FC_Main$estimates[[i]]) +1
}

Y = X-1 

tau_vec <- rep(tau_vec, times = Y)

#Check if the two vectors have the same length so that I can pass them into the AMCE_bound function
length (tau_vec) == length(pi_vec)

bounds <- mapply(AMCE_bound, pi_vec, tau_vec)
bounds
#None of them are over 50%
```

Get the data ready for plotting
```{r}
bound_dat <- as_tibble ( t(bounds) ) %>%
  mutate(x = as.factor( 1:nrow(.)), y = (lower+upper)/2)  #y is the mean of the two bounds
```

Draw an (confidence) interval graph where all the intervals are vertical, next to each other, and in one graph?
```{r}
ggplot(bound_dat, aes(x, y)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) + 
#  theme_minimal() + 
  theme(axis.text.x=element_blank(), axis.title.x=element_blank(), axis.title.y=element_blank()) +
#  ggtitle("Do the AMCE Estimates Infer Majority Preference?") +
  theme(plot.title=element_text( hjust=0.5, vjust=0.0, face='bold')) +
  labs(caption = "* the points represent the means of the two bounds") 

ggsave(file="bounds.eps", width=13, height=10, dpi=300)
```

Average Component Preference (Ganter, 2023)

Load the conjacp function provided from: https://github.com/flavienganter/preferences-conjoint-experiments/blob/main/Functions/conjacp.R

```{r}
#Make sure this file is in the working directory. Use list.files() to check. 
source("conjacp.R")
```

Estimate ACP
```{r}
formula = selected_FC ~ Age + Gender + `Education Level` + Recruitment + `Reputation According to the Troops` + `Military Success` + Crime + `Target of the Crime` + `Type of Involvement in the Crime` + `Attitude Toward the Crime`

unique ( FC$profile ) #1,2
unique ( FC$task ) #1,2,3,4


# Create task variable

data_long         <- FC[order(FC$Response.ID),]

data_long$RespID  <- data_long %>% group_by(Response.ID) %>% group_indices()

data_long$task_fg <- cumsum(!duplicated(data_long[, c("RespID", "task")]))

# Estimate 

conjacp_data <- conjacp.prepdata(formula = formula,
                                 data = data_long,
                                 tasks = "task_fg",
                                 
                                 id = "RespID")

results_acp <- conjacp.estimation(conjacp_data,
                                  estimand = "acp",
                                  adjust = FALSE)
```

```{r}
tabacp <- data.frame(modality = c("Age:", "  25", "  47", "  68" , "", 
                        "Gender:", "   Man", "   Women", "", 
                        "Education Level:", "  Primary School", "  Secondary School", "  Associate Degree","  University", "",
                        "Recruitment:", "  Ideology", "  A job", "  Forced Recruitment", "",
                        "Reputation:", "  Good Example", "  Kind", "  Power-hungry", "  Unjust", "",
                        "Military Success:", "  Won almost all battles", "  Won half of battles", "  Won few battles", "",
                        "Crime:", "  Killing", "  Sexual Violence", "",
                        "Target of the Crime:", "  Enemy Informants", "  People living in an area that supported the enemy", "  People living in an area controlled by the enemy", "",
                        "Involvement in the Crime:", "  Decided to commit on his/her own", "  Did not prevent someone else from committing", "  Followed an order to commit", "  Ordered someone else to commit", "",
                        "Attitude toward the Crime:", "  Reluctant", "  Enthusiastic", ""
                         ),
            var = c("", "Age", "Age", "Age", "",
                    "", "Gender", "Gender", "",
                    "", "Education Level", "Education Level", "Education Level", "Education Level", "", 
                    "", "Recruitment", "Recruitment", "Recruitment","",
                    "", "Reputation", "Reputation", "Reputation", "Reputation", "", 
                    "", "Military Success", "Military Success", "Military Success", "",
                    "", "Crime", "Crime", "",
                    "", "Target of the Crime","Target of the Crime","Target of the Crime","",
                    "", "Involvement in the Crime", "Involvement in the Crime", "Involvement in the Crime", "Involvement in the Crime", "",
                    "", "Attitude toward the Crime", "Attitude toward the Crime", ""),
            estimate = c(1, results_acp$estimates[1:3], 1, 
                         1, results_acp$estimates[4:5], 1, 
                         1, results_acp$estimates[6:9], 1,  #Education Level
                         1, results_acp$estimates[10:12], 1, #Recruitment
                         1, results_acp$estimates[13:16], 1, #Reputation
                         1, results_acp$estimates[17:19], 1, #Military Success
                         1, results_acp$estimates[20:21], 1, #Crime
                         1, results_acp$estimates[22:24], 1, #Target of the Crime
                         1, results_acp$estimates[25:28], 1, #Involvement in the Crime
                         1, results_acp$estimates[29:30], 1  #Attitude toward the Crime
                         ),
            se = c(0, sqrt(diag(results_acp$vcov))[1:3], 0, 
                   0, sqrt(diag(results_acp$vcov))[4:5], 0,
                   0, sqrt(diag(results_acp$vcov))[6:9], 0,
                   0, sqrt(diag(results_acp$vcov))[10:12], 0,
                   0, sqrt(diag(results_acp$vcov))[13:16], 0,
                   0, sqrt(diag(results_acp$vcov))[17:19], 0,
                   0, sqrt(diag(results_acp$vcov))[20:21], 0,
                   0, sqrt(diag(results_acp$vcov))[22:24], 0,
                   0, sqrt(diag(results_acp$vcov))[25:28], 0,
                   0, sqrt(diag(results_acp$vcov))[29:30], 0)
           )
tabacp$modality <- factor(tabacp$modality, levels = unique(tabacp$modality)[length(tabacp$modality):1])
```

Theme by Ganter (2023)
```{r}
theme_fg <- function(base_size = 14, base_family = "Roboto Condensed") {
  update_geom_defaults("bar", list(fill = "grey20"))
  update_geom_defaults("line", list(colour = "grey30"))
  update_geom_defaults("label",
                       list(family = "Roboto Condensed", 
                         face = "plain"))
  update_geom_defaults("text",
                       list(family = "Roboto Condensed",
                            face = "plain"))
  
  ret <- theme_bw(base_size, base_family) +
    theme(panel.background = element_rect(fill = "#ffffff", colour = NA),
          title = element_text(size = rel(1.1), vjust = 1.2, 
                               family = "Roboto Condensed Bold",
                               face = "plain"),
          plot.subtitle = element_text(size = rel(0.8), 
                                       family = "Roboto Condensed",
                                       face = "plain"),
          plot.caption = element_text(margin = margin(t = 10), size = rel(0.6),
                                      family = "Roboto Condensed",
                                      face = "plain"),
          panel.border = element_rect(color = "grey50", fill = NA, size = 0.15),
          panel.spacing = unit(1, "lines"),
          panel.grid.minor = element_blank(),
          panel.grid.major = element_line(size = 0.25, colour = "grey90"),
          axis.line = element_blank(),
          axis.ticks = element_blank(),
          axis.title = element_text(size = rel(0.8), 
                                    family = "Roboto Condensed",
                                    face = "plain"),
          axis.title.y = element_text(margin = margin(r = 10)),
          axis.title.x = element_text(margin = margin(t = 10)),
          legend.position = "bottom",
          legend.title = element_text(size = rel(0.8)),
          legend.key.size = unit(.7, "lines"),
          legend.key = element_blank(),
          legend.spacing = unit(0.1, "lines"),
          strip.text = element_text(size = rel(0.9), hjust = 0,
                                    family = "Roboto Condensed",
                                    face = "plain"),
          strip.background = element_rect(fill = "#ffffff", colour = NA))
  ret
}

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7",
               
               "darkorchid4", "midnightblue", "brown4")

library(hrbrthemes)
import_roboto_condensed()
```


```{r, message=FALSE, warning= FALSE}
commplot <- ggplot(tabacp, aes(y = estimate, x = modality)) +
  coord_flip(ylim = c(-.22, .2)) +
  geom_pointrange(aes(ymin = estimate - 1.96 * se, ymax = estimate + 1.96 * se, color = var),
                  position = position_dodge(width = .5), size = .2) +
  labs(y = "", x = "") +
  theme_fg(base_size = 11) +
  theme(panel.grid.minor = element_blank(),
        axis.text.y = element_text(hjust = 0 , vjust = .5 ),
        legend.position = "none")  +
  scale_shape_manual(values = c(21, 22, 23, 23), name = "") +
  scale_fill_manual(values = cbPalette, name = "") +
  scale_colour_manual(values = cbPalette, name = "")

ggsave("ACP.eps", width=11, height=12.5, dpi=300)
```

